---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub. 

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.

I think one of the most important practices for computational reproducibility mentioned in the article was saving raw data. Saving your raw data without cleaning it up or saving analyzed versions of it creates a source for you and others to go back to over and over again. Since this source is unchanged, your results will be reproducible. R helps with this because it pulls your raw data and allows you to analyze it and save your analyses without changing the original data in any way.

3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 

```{r}
sqrt(4^13)
```

4) Push this homework to the GitHub repository for the homework. 





